### 2010-12-06 report/report.tex
update to report
report - edited problem statemetn

We are using machine learning to design a gait for a quadruped
robot. The robot has an on-board computer, drivers for the motors, and
will have camera feedback. The code so far consists of the robot
class, optimization class, parameterized model, sine model, and camera
feedback.  Both the hardware and software are progressing on schedule.
Some promising gaits have been generated, and we anticipate a final
evaluation of the robots gait in November.

A video presentation of this project should be viewed at http://www.youtube.com/watch?v=ODoiOj9DdGg.
\edit{write this}

\section{Problem definition}
% Precisely define the problem you are addressing (i.e. formally specify
% the inputs and outputs). Elaborate on why this is an interesting and
% important problem.
We are testing several different learning methods to design a gait for 
a quadruped robot from the Cornell Computational Synthesis Lab. The metric 
for evaluation of the designed gait is speed. A comparison and evaluation 
of the many different methods available for optimizing the gait of legged 
robots will be useful for future work on this challenging multidimensional 
control problem.

\edit{flesh this out... more details}

@@

\begin{tabular}{|r|c|c|c|}
\hline
                       & A     & B     & C    \\
\hline
Solution depth ???        & 14    & 54    & 21   \\
\hline
Nodes visited          & 992   & 2405  & 383  \\
\hline
Time to find solution  & 139ms & 451ms & 54ms \\
\hline
\end{tabular}

>>>>

We are using machine learning to design a gait for a quadruped
robot. The code so far consists of the robot
class, optimization class, parameterized model, sine model, and camera
feedback.

A video presentation of this project should be viewed at

http://www.youtube.com/watch?v=ODoiOj9DdGg.
\edit{write this}

\section{Problem definition}
% Precisely define the problem you are addressing (i.e. formally specify
% the inputs and outputs). Elaborate on why this is an interesting and
% important problem.
We are testing several different learning methods to design a parametrized 
gait for a quadruped robot from the Cornell Computational Synthesis Lab. 
The metric for evaluation of the designed gait is speed. Given parameters 
for the current walk and the current time, our code outputs the position
of each of the robot's motors. A comparison and evaluation 
of the many different methods available for optimizing the gait of legged 
robots will be useful for future work on this challenging multidimensional 
control problem.

@@

\begin{tabular}{|r|c|c|c|}
\hline
                                         & A       & B      & C      \\
\hline
Uniform Random Hill Climbing             & 11.37   & 9.44   & 2.69   \\
\hline
Guassian Random Hill Climbing            & 3.10    & 13.59  & 13.40  \\
\hline
Policy Gradient Descent                  & 0.68    & 14.69  & 3.60   \\
\hline
Random                                   & 6.04    & 17.26  & 4.90   \\
\hline
Simplex (Nelder-Mead)                    & 8.51    & 13.62  & 14.83  \\
\hline
Linear Regression                        & 27.58   & 12.51  & 1.95   \\
\hline
SVM Regression                           & ???     & ???    & ???    \\
\hline
Evolutionary Neural Network (HyperNEAT)  & ???     & ???    & ???    \\
\hline
\end{tabular}
